Workflow Part II: Inverse root modeling and post-processing

### 2021-04-13 09.0_manuscript.rmd
Minor corrections

Section  | Word Count  
------------- | -------------  
Summary | 200  
Main Text  | 6934  
Introduction | 831    
Methods |  3150  
Results | 838  
Discussion | 2115  
Keywords | 8

@@

\
Figure \@ref(fig:sp-erd): Modeled effective rooting depth (ERD; mean $\pm$ 1SE in m) for `r  length(erd.sp)` large, canopy species of Barro Colorado Island. A species ERD is defined as the median, across 100 hydrological realizations, of soil layer depth $z$ at which soil water dynamics ($\mathrm{\Psi}_{\textrm{soil,} z}$) best explained observed dynamics of species growth for each realization. As soil layers in the hydrological model are discretely resolved into exponentially increasing depths, so is the ERD axis. Deeper depths are shown with darker blue colors.

\
Figure \@ref(fig:erd-hyd): Modeled effective rooting depth (ERD) versus hydraulic properties for seven canopy species found on Barro Colorado Island (Panama). Spearman's $r$ and significance levels. Linear model fits (blue lines) with confidence bands (gray area) are shown for significant fits at $\alpha$ = 0.05. See Fig. S10 for the full correlation matrix.

\
Figure \@ref(fig:erd-mort-census-evg): Mortality rate (mean $\pm$ 1SE in % yr^-1^) versus modeled effective rooting depth (ERD; mean $\pm$ 1SE in m) for `r nrow(mrate.depth.mean %>% subset(deciduous == "E"))` evergreen, canopy species found on Barro Colorado Island over seven census intervals (1981-2015). $R$^2^ and significance levels for linear model fits are given in panel insets. Model fits (blue lines) with confidence bands (gray area) are only shown for periods with significant fits at $\alpha$ = 0.05 or $\alpha$ = 0.1 (1982-85), identified by census-intervals with a superscript *.

>>>>

Section  | Word Count  
------------- | -------------  
Summary | 200  
Main Text  | 6933  
Introduction | 831    
Methods |  3150  
Results | 838  
Discussion | 2115  
Keywords | 8

@@

\
Figure \@ref(fig:sp-erd): Modeled effective rooting depth (ERD; mean $\pm$ 1SE in m) for `r  length(erd.sp)` large, canopy species of Barro Colorado Island. A species ERD is defined as the median, across 100 hydrological realizations, of soil layer depth $z$ at which soil water dynamics ($\mathrm{\Psi}_{\textrm{soil,} z}$) best explained observed dynamics of species growth for each realization. As soil layers in the hydrological model are discretely resolved into exponentially increasing depths, so is the ERD axis. Species are color coded by leaf habit.

\
Figure \@ref(fig:erd-hyd): Modeled effective rooting depth (ERD) versus hydraulic properties for seven canopy species found on Barro Colorado Island (Panama). Spearman's $r$ and significance levels are given in panel insets. Linear model fits (blue lines) with confidence bands (gray area) are shown for significant fits at $\alpha$ = 0.05. See Fig. S10 for the full correlation matrix. Species are color coded by leaf habit. Multiple species in Facultative Deciduous leaf-habit are distinguished by shapes.

\
Figure \@ref(fig:erd-mort-census-evg): Mortality rate (mean $\pm$ 1SE in % yr^-1^) versus modeled effective rooting depth (ERD; mean $\pm$ 1SE in m) for `r nrow(mrate.depth.mean %>% subset(deciduous == "E"))` evergreen, canopy species found on Barro Colorado Island over seven census intervals (1981-2015). $R$^2^ and significance levels for linear model fits are given in panel insets. Model fits (blue lines) with confidence bands (gray area) are only shown for periods with significant fits. Census intervals, for which fits are significant at $\alpha$ = 0.05 are identified by superscript $**$, while those significant at $\alpha$ = 0.1 by superscript $*$.

### 2021-04-13 Readme.Rmd
Minor corrections

Set-up and run effective rooting depth models, evaluate model, and join ERD from the predicted model with hydraulic traits and mortality data, and calculated realized hydraulic risk

@@

```{r Chunk 10.0, eval = FALSE}
# render("10.0_Supporting_Information.Rmd", output_format = "bookdown::html_document2")
render("10.0_Supporting_Information.Rmd", output_format = "bookdown::word_document2")
```

>>>>

Set-up and run effective rooting depth models, evaluate model, and join ERD from the predicted model with hydraulic traits and mortality data, and calculate realized hydraulic risk

@@

```{r Chunk 10.0, eval = FALSE}
# rmarkdown::render("10.0_Supporting_Information.Rmd", output_format = "bookdown::html_document2")
rmarkdown::render("10.0_Supporting_Information.Rmd", output_format = "bookdown::word_document2")
```
